RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-29 main.tex
:pencil: Update abstract

\begin{document}
\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface}
% \title{UniScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control wireless propagation environment by boosting/suppressing signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
\end{abstract}

@@

	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates scattered component with backscatter information, and the cooperative receiver decodes both links from two propagation paths.

@@

	To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
	The contributions of this paper are summarized as follows.

	\emph{First,} we propose UniScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.

	\emph{Third,} we consider an application scenario where multiple UniScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
	To investigate how UniScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at UniScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.

@@

	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.

@@

\begin{section}{UniScatter}
	Using shared spectrum, energy and infrastructures, UniScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
	In particular, passive UniScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical UniScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{UniScatter Nodes}
		Based on link priority and \gls{csi}, UniScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:uniscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each UniScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of UniScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

		As shown in Fig. \subref*{fi:block_diagram}, UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive UniScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a UniScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fi:uniscatter_node}
		\end{figure*}
	\end{subsection}

	\begin{subsection}{UniScatter Receiver}
		Since each passive UniScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
			}
			\label{fi:energy_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, UniScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
	\end{subsection}

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A single-user multi-node UniScatter system.}
			\label{fi:uniscatter_network}
		\end{figure}
		To demonstrate the advantages of UniScatter, we consider a single-user multi-node \gls{miso} UniScatter system as shown in Fig. \ref{fi:uniscatter_network}.
		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna UniScatter nodes with $M$ reflection states.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.

@@

		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all UniScatter nodes.

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

		As illustrated in Fig. \ref{fi:energy_distribution}, the UniScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.

@@

		\begin{remark}
			Upon successful backscatter decoding, UniScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
			\label{re:backscatter_decision}
		\end{remark}

@@

		\begin{subsubsection}{Coverage Disk Radius}
			Fig. \subref*{fi:region_coverage} shows the relationship between UniScatter cover disk radius and achievable rate regions.
			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
			This is because the product path loss (a.k.a. double fading) model for finite-size scatterers is less severe for such near-far setups.
			Thanks to the dispersed characteristics of UniScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
	% ? Channel estimation error, coordination issues
	\label{se:simulation_results}
\end{section}

>>>>

\begin{document}
\title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	% Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	% \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	% \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
	\gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
	\gls{ris} programs antenna/metamaterial array to adjust the scattering phase shifts and control signal strength in specific directions.
	% \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	% \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
	% \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
	\gls{sr} introduces a passive scatterer to ride secondary information over the primary signal generated by an active transmitter, and employs a co-located receiver to sequentially decode both links.
	% In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
	In this paper, we show how those three seemingly different technologies can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be controlled to partially engineer the wireless channel and partially modulating information onto the scattered wave.
	This contrasts with \gls{bc}/\gls{sr} (resp. \gls{ris}) where states are exclusively a function on information symbols (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.
	% augmented \gls{qos} control.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those three technologies under some specific reflection states; or evolve in a mixed state.
	We show RIScatter is subject to a fundamental tradeoff that balances its information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.
	% Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), RIScatter nodes located at different places adapt the input distribution of passive scatterers based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
	% RIScatter receiver semi-coherently decodes all nodes from accumulated energy, determines primary equivalent channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	% It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	% To accommodate signal characteristics, we also propose a low-complexity RIScatter receiver that preserves the aforementioned benefits.
	% Using shared spectrum, energy, and infrastructures, RIScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	% We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	% Simulation results demonstrate RIScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
	% Simulation results demonstrate RIScatter can flexibly control the tradeoff between backscatter modulation and passive beamforming via smart input distribution design, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.
	% Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming, which
	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, and \gls{ris} as special cases.
	% Simulation results demonstrate RIScatter can exploit smart input distribution design to provide a smooth transition between backscatter modulation and passive beamforming, which outperforms \gls{bc}, \gls{sr}, and \gls{ris}.

	% The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter). Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).

\end{abstract}

@@

	In \gls{sr}, the primary transmitter generates active radio carrying primary information, the secondary node modulates backscatter information onto the scattered wave, and the cooperative receiver decodes both links from two propagation paths.

@@

	To the best of our knowledge, all relevant literatures assumed at backscatter information sources either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a}.
	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
	In this paper, we introduce RIScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and practical receiver design.
	The contributions of this paper are summarized as follows.

	\emph{First,} we propose RIScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) RIScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission; 4) the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

	\emph{Second,} we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.

	\emph{Third,} we consider an application scenario where multiple RIScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
	To investigate how RIScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at RIScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.

@@

	\emph{Fifth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
	It is concluded that 1) RIScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, RIScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable inputs of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the proposed \gls{pgd} beamforming provides larger rate region than \gls{mrt}-based schemes; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.

@@

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:uniscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

		As shown in Fig. \subref*{fi:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fi:uniscatter_node}
		\end{figure*}
	\end{subsection}

	\begin{subsection}{RIScatter Receiver}
		Since each passive RIScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
		Besides, the backscatter symbol period is typically longer than primary due to the load switching speed constraint.
		Those facts imply \emph{backscatter detection} under primary uncertainty can be viewed as part of \emph{primary channel training}.
		Hence, we propose a practical RIScatter receiver that semi-coherently decodes RIScatter nodes from the received energy per backscatter block, re-encodes for their reflection patterns, retrieves primary equivalent channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
			}
			\label{fi:energy_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:energy_distribution}, the total received energy per backscatter block is a random variable that follows different distributions conditioned on different input state hypotheses.
		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, RIScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
	\end{subsection}

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A single-user multi-node RIScatter system.}
			\label{fi:uniscatter_network}
		\end{figure}
		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:uniscatter_network}.
		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed RIScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.

@@

		Let $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all RIScatter nodes.

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of RIScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

		As illustrated in Fig. \ref{fi:energy_distribution}, the RIScatter receiver divides the received energy space into disjoint decision regions associated with those hypotheses.

@@

		\begin{remark}
			Upon successful backscatter decoding, RIScatter receiver can always re-encode node messages to recover their reflection patterns at each primary block.
			Therefore, backscatter decision design has no impact on the primary achievable rate, and any thresholding scheme maximizing the total backscatter mutual information \eqref{eq:backscatter_mutual_information} is also optimal for problem \eqref{op:decision_threshold}.
			\label{re:backscatter_decision}
		\end{remark}

@@

		\begin{subsubsection}{Coverage Disk Radius}
			Fig. \subref*{fi:region_coverage} shows the relationship between RIScatter cover disk radius and achievable rate regions.
			We observe both primary and backscatter performance are enhanced when nodes are dropped closer to the user.
			This is because the product path loss (a.k.a. double fading) model for finite-size scatterers is less severe for such near-far setups.
			Thanks to the dispersed characteristics of RIScatter nodes and legacy users, each node can simply scatter and be decoded by the closest user, thus avoids the development optimization and allows uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
	% ? Channel estimation error, coordination issues
	\label{se:simulation_results}
\end{section}
